\ttitle

### 2013-10-29 Chapters/Chapter3/one_class_svm.tex
Fix missing vertical bar
Wip: chapter 3 formulas, chapter 4 model construction and properties

In the maximization of Equation \ref{eq:svdd_lagrange} a large fraction of the multipliers $\alpha_i$ become zero and for a small fraction $\alpha_i > 0$.
This small fraction, for which $\alpha_i$ is non-zero, are called the \glspl{sv} and these objects lie on the boundary of the description.
The center of the hypersphere only depends on this small number of \glspl{sv} and the objects for which $\alpha_i = 0$ can be disregarded from the solution.
Testing the membership of a (new) object $\vectorsym{z}$ is done by determining if the distance to the center $\vectorsym{a}$ of the sphere is equal or smaller to the radius $R$:
\begin{equation}
  \lvert \vectorsym{z} - \vectorsym{a} \rVert ^2 = (\vectorsym{z} \cdot \vectorsym{z}) - 2 \sum_{i} \alpha_i(\vectorsym{z} \cdot \vectorsym{x}_i) + \sum_{i,j}(\vectorsym{x}_i \cdot \vectorsym{x}_j) \le R^2
\end{equation}

@@

@@

@@

-- Quotes and refs to use --
$k(\mathbf{x}_i, \mathbf{x})$ is a kernel function computing a dot product in feature space, introduced by Aizerman \etal \cite{aizerman1964theoretical}.
``Training a \gls{svm} with Gaussian \gls{rbf} kernels corresponds to minimizing the specific cost function with a regularization operator'' \cite{smola1998connection}. \\
``Gaussian kernels tend to yield good performance under general smoothness assumptions and should be considered especially of no additional knowledge of the data is available.'' \cite{smola1998connection}. \\
``Choosing a small width of the kernels leads to high generalization error as it effectively decouples the separate basis functions of the kernel expansion into very localized functions which is equivalent to memorizing the data, whereas a wide kernel tends to oversmooth.'' \cite{smola1998connection}. \\

sparsity, RKHS: \cite{girosi1998equivalence}

@@

In case of a \gls{rbf} kernel, the width parameter $\sigma$ determines the flexibility and complexity of the boundary.
The value of this parameter greatly determines the outcomes of the algorithm (\eg \gls{svdd}) as illustrated in Figure \ref{fig:svdd-boundary}.
With a small value for the kernel width $\sigma$, each data point will tend to be used as a support vector and will represent a small Gaussian.
The solution then corresponds with standard non-parametric density estimation.
With a large value for the width $\sigma$, the boudary approximates the spherical boundary.

@@

>>>>

In the maximization of Equation \ref{eq:svdd_lagrange} a large fraction of the multipliers $\alpha_i$ become zero and for a small fraction $\alpha_i > 0$.
This small fraction, for which $\alpha_i$ is non-zero, are called the \glspl{sv} and these objects lie on the boundary of the description.
The center of the hypersphere only depends on this small number of \glspl{sv} and the objects for which $\alpha_i = 0$ can be disregarded from the solution.
Testing the membership of a (new) object $\vectorsym{z}$ is done by determining if the distance to the center $\vectorsym{a}$ of the sphere is equal or smaller to the radius $R$:
\begin{equation}\label{eq:svdd_test_object}
  \lVert \vectorsym{z} - \vectorsym{a} \rVert ^2 = (\vectorsym{z} \cdot \vectorsym{z}) - 2 \sum_{i} \alpha_i(\vectorsym{z} \cdot \vectorsym{x}_i) + \sum_{i,j}(\vectorsym{x}_i \cdot \vectorsym{x}_j) \le R^2
\end{equation}

@@

Because the Gaussian \gls{rbf} often yields good (\ie tight) boundaries, this set of kernels fuctions is commonly used:
\begin{equation}
  (\vectorsym{x} \cdot \vectorsym{y}) \rightarrow K(\vectorsym{x},\vectorsym{y}) = \operatorname{exp}\left(- \frac{\lVert \vectorsym{x} - \vectorsym{y} \rVert ^2}{\sigma^2}\right)
\end{equation}
Using this kernel function, the Lagrangian error function $L$ of Equation \ref{eq:svdd_lagrange} changes to:
\begin{equation}\label{eq:svdd_lagrange_kernel}
  L = 1 - \sum_{i} \alpha_i^2 - \sum_{i \ne j} \alpha_i \alpha_j K(x_i, x_j)
\end{equation}
Using Equation \ref{eq:svdd_test_object}, the following kernel formulation needs to hold for a new object $\vectorsym{z}$ to lie within the hypersphere:
\begin{equation}\label{eq:svdd_inequality}
  \sum_{i} \alpha_i K(\vectorsym{z}, x_i) \le \frac{1}{2} \left( 1 - R + \sum_{i,j} \alpha_i \alpha_j K(x_i, x_j) \right)
\end{equation}

@@

\begin{figure}
  \centering
    \includegraphics[width=0.8\textwidth,keepaspectratio]{./Figures/chapter3/svdd-parameter-sigma.pdf}
  \caption[\gls{svdd} boundary]{The \gls{svdd} method trained on a banana-shaped data set with different $\sigma$-values for the \gls{rbf} kernel. Solid circles are support vectors, the dashed line is the boundary.}
  \label{fig:svdd-boundary-sigma}
\end{figure}

\TODO{Use Figure \ref{fig:svdd-boundary} or \ref{fig:svdd-boundary-sigma}?}

@@

-- Quotes and refs to use --
$k(\mathbf{x}_i, \mathbf{x})$ is a kernel function computing a dot product in feature space, introduced by Aizerman \etal \cite{aizerman1964theoretical}.
``Training a \gls{svm} with Gaussian \gls{rbf} kernels corresponds to minimizing the specific cost function with a regularization operator'' \cite{smola1998connection}. \\

``Gaussian kernels tend to yield good performance under general smoothness assumptions and should be considered especially of no additional knowledge of the data is available.'' \cite{smola1998connection}. \\

``Choosing a small width of the kernels leads to high generalization error as it effectively decouples the separate basis functions of the kernel expansion into very localized functions which is equivalent to memorizing the data, whereas a wide kernel tends to oversmooth.'' \cite{smola1998connection}. \\

``For small values of $\sigma$ almost all $\alpha_i >0$ and the \gls{svdd} resembles a Parzen density estimation.'' \cite{tax2002uniform} page 4, \cite{tax1999support} page 4. \\

sparsity, RKHS: \cite{girosi1998equivalence} \\

Kernels for Support Vector Classifiers where first (?) used by Vapnik \cite{vapnik1998statistical}.

@@

In case of a \gls{rbf} kernel, the width parameter $\sigma$ determines the flexibility and complexity of the boundary.
The value of this parameter greatly determines the outcomes of the algorithm (\eg \gls{svdd}) as illustrated in Figure \ref{fig:svdd-boundary}.
With a small value for the kernel width $\sigma$, each data point will tend to be used as a support vector (for almost all $\alpha_i > 0$) and the \gls{svdd} solution resembles a Parzen density estimation.
For large values of $\sigma$, the solution will resemble the original hypersphere solution is obtained (in contrast with a tight boundary around the data).
With a large value for the width $\sigma$, the boudary approximates the spherical boundary.

@@

-- Notes --
\begin{itemize}
  \item Low target rejection rate $f_{T-}$ and low outlier acceptance rate $f_{O+}$. When only target examples are present, the first one can be estimated by the number of support vectors that we obtain as a solution of Lagrangian \ref{eq:svdd_lagrange_kernel}.
\end{itemize}

### 2013-10-29 Chapters/Chapter4/model_construction.tex
Wip: chapter 3 formulas, chapter 4 model construction and properties

% !TEX root = ../../main.tex
\section{Model Construction: Incremental SVDD}\label{sec:method_model_construction}
After the data is collected and pre-processed (or in the case of the artificial data sets: generated), we construct an online incremental sliding window model construction algorithm.
We follow the method and implementation introduced by Tax and Laskov \cite{tax2003online}, the \acrlong{isvdd} method.
This method combines the techniques of online, unsupervised and incremental learning methods with the earlier introduced \gls{oc-svm} algorithm \gls{svdd}.
The method is first initialized with a window length and then in every step a new data object is added to and the last data object is removed from the working set.

@@

From experiments it shows that the online, \gls{isvdd}, method results in less false alarms than the static \gls{svdd}.
An explanation for this is that \gls{isvdd} follows the changing data distribution, such that small changes over time, like a drift in mean or increase in frequency, continuously re-model the \gls{svm} representation.

>>>>

% !TEX root = ../../main.tex
\section{Model Construction: Incremental SVDD}\label{sec:method_model_construction}
After the data is collected and pre-processed (or in the case of the artificial data sets: generated), we construct an online incremental sliding window algorithm.
We follow the method and implementation introduced by Tax and Laskov \cite{tax2003online}, the \acrlong{isvdd} method.
This method combines the techniques of online, unsupervised and incremental learning methods with the earlier introduced \gls{oc-svm} algorithm \gls{svdd}.
The method is first initialized with a window length and then in every step a new data object is added to and the last data object is removed from the working set.

@@

From experiments it shows that the online, \gls{isvdd}, method results in less false alarms than the static \gls{svdd}.
An explanation for this is that \gls{isvdd} follows the changing data distribution, such that small changes over time, like a drift in mean or increase in frequency, continuously re-model the \gls{svm} representation.
For our method we use the re-modeling capability of the \gls{isvdd} algorithm to obtain change indication measure.
The following section will discuss the properties used from the constructed \gls{oc-svm} model at every loop-step of the algorithm.

### 2013-10-29 Chapters/Chapter4/model_properties.tex
Wip: chapter 3 formulas, chapter 4 model construction and properties

>>>>

-- Notes --
\begin{itemize}
  \item Error measure of \gls{svdd} is based on both volume of the sphere and number of outliers.
  \item When the outliers are uniformly distributed around the target data, we should minimize the volume of the description.
  \item To do this (minimize the volume) we need to estimate the volume.
  \item \cite{tax2002uniform} states that when the outliers are uniformly distributed, the fraction of outliers that is accepted gives an estimate of the volume of the target data description (with respect to the volume of the outlier distribution).
  \item When the fraction of outlier is kept constant (by the parameters $C$ and $\sigma$), and when it is known that more outliers are present in current working set, the volume must increase.
  \item Equation \ref{eq:svdd_inequality} gives that the right term must increase for a larger volume, \ie the value of $R$ will increase.
  \item Thus, an increase of value $R$ indicates an increase of outliers in the working set.
  \item This indicates a possible new activity in the time series data.
\end{itemize}

In the previous section we have discussed the \gls{isvdd} method, which creates a \gls{oc-svm} representation of a working set of data objects at every step of the algorithms loop.
This section shows how we interpret the constructed model, to obtain a measure which can be used for a indication of change points.
How this obtained measure is used to indicate a change is discussed in the following section.

The \gls{isvdd} algorithm creates a spherical \gls{oc-svm} representation of the working set at every step of the algorithm.
This model is obtained by the minimization of Equation \ref{eq:svdd_objective}, which incorporates the radius $R$ of the sphere and the distances $\vectorsym{\xi}$ from the outliers to the boundary.
We will use the the radius $R$ of the hypersphere as an indication of change.

In \cite{tax2002uniform} Tax and Duin provide an analysis of the error of the \gls{svdd} algorithm.
This error is based on
\begin{inparaenum}[\itshape 1\upshape)]
\item the fraction $f_{T-}$ of target objects that is rejected, and
\item the fraction $f_{O+}$ of outliers that is accepted.
\end{inparaenum}
Since in \gls{occ} situation typically there are (almost) no examples of outlier objects, Tax and Duin construct a method to generate outliers, based on the assumption that the outliers are uniformly distributed around the target set.
To minimize the error, calculated by the fractions $f_{T-}$ and $f_{O-}$, we should minize the volume of the target data description (\ie the boundary of \gls{svdd}).
This is since the the fraction of accepted outliers $f_{O-}$ is an estimate of the volume of the target data description, with respect to the volume of the outlier distribution.
Tax and Duin provide a method to optimize the parameters of the \gls{svdd} method, being the trade-off parameter $C$ and the \gls{rbf} kernel width $\sigma$.
This optimization will result in the modification of the radius $R$ of Equation \ref{eq:svdd_objective} and affects the Lagrangian inequality \ref{eq:svdd_inequality}.

\TODO{outliers is kept constant, thus Radius must increase}
